An Autonomous and Decentralized Data Marketplace for Trusted Machine Economy $^{\dagger}$

### 2019-12-31 paper.tex
Distinguish from the prior work
Tweak wording

%=================================================================
% Full title of the paper (Capitalized)
\Title{Decentralized Data Marketplace to Enable Trusted Machine Economy $^{\dagger}$}

@@

\subsubsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing. We employed repeated games to build our game theory model. Repeated games consists of several repetitions of the same base game which meets the scenario of data subscription.

@@

\section{Results}
It is important to claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle. Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle. Therefore, in the following evaluations, all devices run with client library only.

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{An Autonomous and Decentralized Data Marketplace for Trusted Machine Economy $^{\dagger}$}

@@

\subsubsection{Game Theory Adoption}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing. We employed repeated games to build our game theory model. Repeated games consists of several repetitions of the same base game which meets the scenario of data subscription.

@@

\section{Evaluations}
It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle. Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle. Therefore, in the following evaluations, all devices run with client library only.
